### 2022-10-12 dissertation/chapters/01-introduction.tex
✨ (dissertation): Chapter 2 WIP

\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today. In recent years, \ac{ML} research has seen some notable achievements in academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.

@@

By achieving the objectives outlined above, a number of research contributions are made. These contributions are presented in this following section.

@@

This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:

@@

To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.

>>>>

\noindent
\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today. In recent years, \ac{ML} research has seen some notable achievements in academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.

@@

\noindent
By achieving the objectives outlined above, a number of research contributions are made. These contributions are presented in this following section.

@@

\noindent
This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:

@@

\noindent
To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.
